S-process Enhancement in Barium Disk Stars

### 2018-01-21 article/ms.tex
analy

\section{Introduction}

@@

@@

Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA. Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star. Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}. During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.

@@

To John Power, hold in there buddy

>>>>

\section{Introduction} \label{sec:intro}

@@

Barium stars are optimal sites for investigating the relationship between the neutron-capture elements and other species that may be
depleted or enhanced, because they act as neutron seeds during the operation of the s-process. In the ABG phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star. In an identical mechanism to the presence of s-process elelment enhancement, carbon enhanced stars exist intrinsically or extrinsically. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. In our sample of barium star candidates we discovered enhancement in both CH and the G band for 178 of our total 257 stars. \todo{maybe put a list of the stars ?}

@@

Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA. Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star. Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}. During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
\todo{maybe put a list of the stars ?}

@@

Fired Status: yes
